\documentclass[a4paper,12pt]{article}
%\documentclass[a4paper,12pt]{amsart}
\author{Don Knuth}
\title{The \TeX\ Book}
\date{\today}
\usepackage{amsmath}
\usepackage{amsthm}
\begin{document}
\maketitle
\section{Special characters}

\textbf{Exercise 6.} \textit{Prove Fermat's Theorem.}
See table~\ref{tab:test} on page~\pageref{tab:test}.
\subsection{Accents}
\begin{tabular}{l r r r c} 
Name&Exam1&Exam2&Exam3&Grade\\
John&19& 28&33&C \\
Jane&49& 35&60&B  \\
Jim&76& 38&59&A 
\end{tabular}

\begin{table}
\begin{center}
\begin{tabular}{| l || r | r | r | c |}  
\hline
Name&Exam1&Exam2&Exam3&Grade\\
\hline\hline
John&19& 28&33&C \\  
\hline
Jane&49& 35&60&B  \\
\hline
Jim&76& 38&59&A  \\
\hline
\end{tabular}
\caption{Math 361 Grades\label{tab:test}} 
\end{center}
\end{table}

\subsection{Braces}
$\mathbf{R}$

\smallskip
\noindent\textbf{Fermat's Last Theorem.}
\textit{For $n\ge3$, 
the equation $x^n+y^n=z^n$ has no non-trivial integer solutions.}
\smallskip
\begin{proof} See Wiles.
\end{proof}

\begin{itshape}
The polynomial $p(t)$ splits...
\end{itshape}

\subsection{Dollar signs}
\[
\left|\sum_{i=1}^n (\quad's) a_ib_i\right|
\le
\left(\sum_{i=1}^n a_i^2\right)^{1/2}
\left(\sum_{i=1}^n b_i^2\right)^{1/2}
\]

\section{Sectioning}
\begin{center}123 \end{center}
\begin{quote} 345\end{quote}

\begin{itemize}
\item This is the first item
\item This is the second item
\item This is the last itme
\end{itemize}

\smallskip
\textbf{Some special characters in TeX:}\cite{hA70,eM57}
\begin{enumerate}
\item Accents  
\item Braces 
\item Dollar signs 
\end{enumerate}

\begin{equation}
\sum_{k=1}^n k^2, \frac{a}{q}, \int_1^x\frac{1}{x}dx, \sin(x), \arcsin(x), e^{2 \pi i}
\end{equation}
\begin{align*} 
(a+b)^3 &= (a+b)^2(a+b)\\
&=(a^2+2ab+b^2)(a+b)\\
&=(a^3+2a^2b+ab^2) + (a^2b+2ab^2+b^3)\\
&=a^3+3a^2b+3ab^2+b^3
\end{align*}
\section{Conclusion}
1d23

\begin{thebibliography}{99}
\bibitem{hA70}
Henry~H. Albert,
\emph{Free torsoids},
Current trends in lattice theory.
D.~Van Nostrand, 1970.
\bibitem{hA70a}
Henry~H. Albert,
\emph{Free torsoids},
Current trends in lattice theory
(G.\,H. Birnbaum, ed.).
vol.~7, D.~Van Nostrand, Princeton, January, 1970,
no translation available, pp.~173--215 (German).
\bibitem{sF90}
Soo-Key Foo,
\emph{Lattice Constructions},
Ph.D. thesis, University of Winnebago, 1990.
262
Chapter 10 LATEX documents
\bibitem{sF90a}
Soo-Key Foo,
\emph{Lattice Constructions},
Ph.D. thesis, University of Winnebago, Winnebago, MN,
December 1990, final revision not yet available.
\bibitem{gF86}
Grant~H. Foster,
\emph{Computational complexity in lattice theory},
tech. report, Carnegie Mellon University, 1986.
\bibitem{gF86a}
Grant~H. Foster,
\emph{Computational complexity in lattice theory},
Research Note 128A, Carnegie Mellon University,
Pittsburgh, PA, December, 1986,
research article in preparation.
\bibitem{pK69}
Peter Konig,
\emph{Composition of functions}.
Proceedings of the Conference on Universal Algebra
(Kingston, 1969).
\bibitem{pK69a}
Peter Konig,
\emph{Composition of functions}.
Proceedings of the Conference on Universal Algebra
(G.~H. Birnbaum, ed.).
vol.~7, Canadian Mathematical Society,
Queen’s Univ., Kingston, ON,
available from the Montreal office,
pp.~1--106 (English).
\bibitem{wL75}
William~A. Landau,
\emph{Representations of complete lattices},
Abstract: Notices Amer. Math. Soc. \textbf{18}, 937.
\bibitem{wL75a}
William~A. Landau,
\emph{Representations of complete lattices},
Abstract: Notices Amer. Math. Soc. \textbf{18}, 937,
December, 1975.
\bibitem{gM68}
George~A. Menuhin,
\emph{Universal algebra}.
D.~Van Nostrand, Princeton, 1968.
10.5 Back matter
263
\bibitem{gM68a}
George~A. Menuhin,
\emph{Universal algebra}. 2nd ed.,
University Series in Higher Mathematics, vol.~58,
D.~Van Nostrand, Princeton,
March, 1968 (English), no Russian translation.
\bibitem{eM57}
Ernest~T. Moynahan,
\emph{On a problem of M. Stone},
Acta Math. Acad. Sci. Hungar.
\textbf{8}~(1957), 455--460.
\bibitem{eM57a}
Ernest~T. Moynahan,
\emph{On a problem of M. Stone},
Acta Math. Acad. Sci. Hungar.
\textbf{8}~(1957), 455--460
(English), Russian translation available.
\end{thebibliography}

\end{document}
